Download data

### 2024-02-16 scripts/subsetDataforCrews.Rmd
reworked project directory writing fn from last year SOS_gb

@@

blm_surf <- st_read(paste0(p, 'Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp'), quiet = TRUE)
usfs_surf <- st_read(paste0(p, 'Public_land_ownership/USFS_West_simplified/USFS_West_simplified.shp'), quiet = TRUE)
invasives <- rast(paste0(p, 'MRLC/', '2023_InvGrassCover.tif'))
change_intensity <- rast(paste0(p, 'MRLC/total_change_intensity_index/', 'TCII_3arc.tif'))
fire_perimeters <- st_read( quiet = T,
  paste0(p, 'NIFC_perimeters/', 'InterAgencyFirePerimeterHistory_All_Years_View-Simplified.shp'))
SWSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'desertSW/desert_southwest_provisional_seed_transfer_zones_USGS.shp')) %>% 
  select(seed_zone = Zone) %>% 
  mutate(Dataset = 'SWSTZ', .before = geometry, seed_zone = as.character(seed_zone))
BOWERSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'WWETAC_STZ/GB_2013_revised_reduced.shp')) %>% 
  select(seed_zone) %>% 
  mutate(Dataset = 'BowerRevised', .before = geometry)
STZ <- bind_rows(BOWERSTZ, SWSTZ)
roads <- st_read(quiet = T, paste0(p, 'blmRoadsSOS24/processed/BLM_roads.shp'))
admin_boundaries <- st_read(paste0(p, 'Public_land_ownership/BLM_ADMU/BLM_ADMU_BOUNDARIES.shp'), quiet = TRUE)
allotments <- st_read(
  file.path(p, 'Public_land_ownership/BLM_Natl_Grazing_Allotment_Polygons/Allotment-simp.shp'))

@@

lapply(teams_list, project_maker,
       target_species = spp_needed,
       blm_surf = blm_surf,
       fs_surf = usfs_surf, 
       fire = fire_perimeters,
       invasive = invasives,
       total_change = change_intensity,
      # sdm_stack, 
       occurrences = occurrences,
      # historic_SOS, 
       roads = roads, seed_transfer = STZ)

>>>>

spp_needed <- read.csv('../data/raw/contract_lkp.csv') %>% 
  left_join(spp_needed, ., by = c('contract' = 'Contract_colloquial')) %>% 
  select(-contract)
```

@@

blm_surf <- st_read(paste0(p, 'Public_land_ownership/BLM_West_simplified/BLM_West_simplified.shp'), quiet = TRUE)
usfs_surf <- st_read(paste0(p, 'Public_land_ownership/USFS_West_simplified/USFS_West_simplified.shp'), quiet = TRUE)
invasives <- rast(paste0(p, 'MRLC/', '2023_InvGrassCover.tif'))
change_intensity <- rast(paste0(p, 'MRLC/total_change_intensity_index/', 'TCII_3arc.tif'))
fire_perimeters <- st_read( quiet = T,
  paste0(p, 'NIFC_perimeters/', 'InterAgencyFirePerimeterHistory_All_Years_View-Simplified.shp'))
SWSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'desertSW/desert_southwest_provisional_seed_transfer_zones_USGS.shp')) %>% 
  select(seed_zone = Zone) %>% 
  mutate(Dataset = 'SWSTZ', .before = geometry, seed_zone = as.character(seed_zone))
BOWERSTZ <- st_read( quiet = T,
  paste0(p, 'provisional_SeedTransferZones/', 'WWETAC_STZ/GB_2013_revised_reduced.shp')) %>% 
  select(seed_zone) %>% 
  mutate(Dataset = 'BowerRevised', .before = geometry)
STZ <- bind_rows(BOWERSTZ, SWSTZ) %>% 
  st_transform(5070)
roads <- st_read(quiet = T, paste0(p, 'blmRoadsSOS24/processed/BLM_roads.shp'))
admin_boundaries <- st_read(paste0(p, 'Public_land_ownership/BLM_ADMU/BLM_ADMU_BOUNDARIES.shp'), quiet = TRUE)
allotments <- st_read(
  file.path(p, 'Public_land_ownership/BLM_Natl_Grazing_Allotment_Polygons/Allotment-simp.shp')) %>% 
  select(ALLOT_NAME)

@@

lapply(teams_list, project_maker,
       admu = admin_boundaries, 
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
      # historic_SOS, 
       roads = roads, seed_transfer = STZ)

ob <- st_read('/media/steppe/hdd/2024SOS_CrewGeospatial/Eastern Mojave - P102073/Geodata/Species/SDM/Salazaria_mexicana.shp')
